### 2022-12-19 source/paper1.tex
reorganizatin for reproducibility

\textbf{Key words}: Power, replication studies, sceptical $p$-value, shrinkage,
two-trials rule, type I error rate

@@

\begin{center}
\begin{figure}[!h]
\begin{center}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

{\centering \includegraphics[width=\maxwidth]{images/paper1/fig1-1}

\end{knitrout}
\caption{Example of the assessment of replication success. The original study
  from \citet{Pyc2010} has effect estimate $\hat \theta_o= 0.4$ on Fisher's $z$
  scale (95\% CI from $0.05$ to $0.74$) and one-sided $p$-value $p_o = 0.011$.
  The left part of the figure illustrates the reverse-Bayes derivation of the
  sufficiently sceptical prior based on the original study result and the
  posterior with lower credible limit fixed at zero. The comparison of the
  sufficiently sceptical prior with the replication study result
  ($\hat \theta_r = 0.15$, 95\% CI from 0.04 to 0.26, $p_r = 0.004$) in the
  right part of the figure is used to assess potential prior-data conflict.}
  \label{fig1:fig1}
\end{center}
\end{figure}
\end{center}

@@

The actual value of $p_{\mbox{\scriptsize Box}}$ is difficult to interpret as it
depends on the level $\alpha$ and does not even exist if the original $p$-value
$p_o$ exceeds $\alpha$. However, \citet{Held2020} showed that if both
$\sign(z_o)=\sign(z_r)$ and
\begin{equation}\label{eq1:extrinsic.p}
\left({z_o^2}/{z_{{\alpha_S}}^2}-1 \right) \left({z_r^2}/{z_{{\alpha_S}}^2}
- 1 \right) \geq c
\end{equation}
hold, replication success at level ${\alpha_S}$ is achieved, where
$z_{{\alpha_S}} = \Phi^{-1}(1-{\alpha_S})$. The requirement
\eqref{eq1:extrinsic.p} can be assessed for any value of
${{\alpha_S}} > \max\{p_o, p_r\}$ and of particular interest is the smallest
possible value of $\alpha_S$ where \eqref{eq1:extrinsic.p} holds, the so-called
\textit{sceptical $p$-value} $p_S$. We are thus interested in the value $z_S^2$
that fulfills
\begin{equation}\label{eq1:extrinsic.p2}
\left({z_o^2}/{z_{S}^2}-1 \right) \left({z_r^2}/{z_{S}^2}
- 1 \right) = c.
\end{equation}
There is a unique solution of \eqref{eq1:extrinsic.p2} which defines the
one-sided {sceptical $p$-value} $p_S= 1-\Phi\left({z_S}\right)$ where
$z_{S} \coloneqq + \surd z_{S}^2$, provided $\sign(z_o)=\sign(z_r)$ holds.
Replication success at level $\alpha_S$ is then achieved if $p_S \leq \alpha_S$.
In the introductory example based on the original study by \citet{Pyc2010}, the
sceptical $p$-value turns out to be $p_S=0.11$.

The sceptical $p$-value has a number of interesting properties, see
\citet[Section 3.1]{Held2020} for details. In particular,
$p_S > \max\{p_o, p_r\}$ always holds with $p_S \downarrow \max\{p_o, p_r\}$ for
$c \downarrow 0$. Furthermore, if the $p$-values $p_o$ and $p_r$ are fixed, the
sceptical $p$-value $p_S$ increases with decreasing relative effect size $d$.
The first property ensures that both the original and the replication study have
to be sufficiently convincing on their own to achieve replication success. The
second property guarantees that shrinkage of the replication effect estimate is
penalized.

The level for replication success $\alpha_S$ has to be distinguished from the
significance level $\alpha$ associated with the ordinary $p$-value.
\citet{Held2020} has used the \textit{nominal level} for replication success
($\alpha_S=\alpha$) for convenience, but in the following we will propose a
recalibration of the procedure along with a new value for $\alpha_S$, the
\textit{golden level} (Section~\ref{sec1:goldenthresh}). The derivation is based
on a property of the required relative effect size for replication success, if
the relative sample size is very large (Section~\ref{sec1:res}). In a nutshell,
the golden level ensures that for original studies which were only borderline
significant ($p_o=\alpha$), replication success is only possible if the
replication
effect estimate is larger than the original one ($d > 1$).\\

\subsection{Relative effect size}\label{sec1:res}
Without loss of generality we now assume that $\hat \theta_o > 0$ and that
$p_o < {\alpha_S}$ has been observed in the original study, otherwise it would
be impossible to achieve replication success at level $\alpha_S$ because $p_S$
is always larger than $p_o$. The condition \eqref{eq1:extrinsic.p} for
replication success can then be re-written as
\begin{equation}\label{eq1:eq.z}
  z_r \geq   z_{{\alpha_S}} \sqrt{1+c/(K-1)} \eqqcolon  \zrmin,
\end{equation}
where $K=z_o^2/z_{{\alpha_S}}^2>1$. The right hand-side of \eqref{eq1:eq.z} is
the minimum replication $z$-value $\zrmin$ required to achieve replication
success. Note that $\zrmin$ increases with increasing $c$, so increasing the
replication sample size leads to a more stringent success requirement $z_r$ and
the corresponding replication $p$-value $p_r$.

@@

\subsection{The golden level}\label{sec1:goldenthresh}
Significance of both the original and the replication study at level $\alpha$ is
a necessary but not sufficient requirement for replication success at the
nominal level ($\alpha_S = \alpha$). The nominal level may therefore be too
stringent. It is more reasonable to calibrate the procedure in such a way that
to establish replication success, original and replication study do not both
necessarily need to be significant at level $\alpha$, provided that the
replication effect estimate does not shrink compared to the original one. We
therefore choose a level $\alpha_S$ such that a borderline significant original
study ($p_o = \alpha$) cannot lead to replication success if there is shrinkage
$s > 0$ of the replication effect estimate. Mathematically, this translates to
setting $\dinfty = 1$ and \mbox{$K = z_\alpha^2/z_{\alpha_S}^2$}
in~\eqref{eq1:smallestpossible} and leads to the quadratic equation $K(K-1) = 1$
with solution $K = \varphi$ where \mbox{$\varphi = (\sqrt{5}+1)/2 \approx 1.62$}
is known as the golden ratio. Solving for $z_{\alpha_S}$ gives
$z_{\alpha_S} = z_\alpha / \sqrt{\varphi}$ and the corresponding \textit{golden
  level}
\begin{eqnarray}\label{eq1:golden}
\alpha_S & = & 1 -  \Phi(z_\alpha / \sqrt{\varphi} )
\end{eqnarray}
for replication success. This is our recommended default choice to assess
replication success and we will study its properties in the following in more
detail. For $z_\alpha = 1.96$ (one-sided $\alpha = 0.025$), the golden level is
$\alpha_S =0.062$. In the introductory example shown in Figure \ref{fig1:fig1},
the sceptical $p$-value is $p_S=0.11 > 0.062$, so the replication of the
\citet{Pyc2010} study was not successful.

The golden level \eqref{eq1:golden} is derived from~\eqref{eq1:smallestpossible}
with $\dinfty = 1$. However, we may also use a different value for the limiting
relative effect size $\dinfty$, say $\dinfty=0.8$. Then replication success is
only possible for a borderline significant result ($p_o = \alpha$) if there is
less than $1-\dinfty$ (20\% for \mbox{$\dinfty=0.8$}) shrinkage of the
replication effect estimate. This approach is equivalent to a limiting relative
effect size of 1 if the original $p$-value $p_o$ is equal to a different level
$\alpha'$, which can be derived as follows: First, solving
\eqref{eq1:smallestpossible} for $\dinfty > 0$ gives
$K = z_\alpha^2/z_{\alpha_S}^2 = 1/2+\sqrt{1/4 + 1/\dinfty^2}$. The new
level~$\alpha'$ fulfills $\varphi=z_{\alpha'}^2/z_{\alpha_S}^2$, so
$z_\alpha^2/K=z_{\alpha'}^2/\varphi$ and therefore
\begin{equation}\label{eq1:alphaPrime}
\alpha' = 1-\Phi\left(z_{\alpha} \, \sqrt{\varphi / K} \right).
\end{equation}
For example, for $\alpha = 0.025$ and $\dinfty = 0.8$ we obtain $\alpha'=0.033$.

@@

The condition $p_S \leq \alpha_S$ for replication success at the golden level is
equivalent to $z_S \geq z_\alpha / \sqrt{\varphi}$, \ie{}
$z_S \sqrt{\varphi} \geq z_\alpha$. In practice it may be preferable to
recalibrate the sceptical $p$-value \mbox{$p_{S} = 1 - \Phi(z_S)$} to
$ \tilde{p}_S = 1 - \Phi(z_S \sqrt{\varphi})$, which then needs to be compared
to $\alpha$ (rather than $\alpha_S$) to assess replication success and can thus
be interpreted on the same scale as an ordinary $p$-value. For example, the
recalibrated sceptical $p$-value for the replication of \citet{Pyc2010} turns
out to be $\tilde{p}_S=0.061$ and does not lead to replication success at any
level $\alpha<0.061$, including the standard $0.025$ level.

@@

{\centering \includegraphics[width=\maxwidth]{images/paper1/fig2-1}

\end{knitrout}
\caption{Comparison of replication success at the golden level
  ($p_S \leq \alpha_S = 0.062$) and the two-trials rule ($p_o \leq 0.025$ and
  $p_r \leq 0.025$). The dotted areas indicate that success is impossible for
  original $p$-value $p_o$ and relative effect size $d$. In the white areas
  success is possible and depends on the relative sample size $c$ as indicated
  by the grey lines. The dashed black line in the left plot indicates the
  limiting relative effect size $\dinfty$. }
\label{fig1:fig2}
\end{figure}

@@

For $c=1$, \citet[Section 3]{Held2020} showed that $z_S^2$ in
\eqref{eq1:extrinsic.p2} simplifies to half the harmonic mean of the squared test
statistics $z_o^2$ and $z_r^2$. The connection $z_S^2 = z_H^2/4$ to the harmonic
mean $\chi^2$-test statistic $z_H^2$ \citep{Held2020b}, which has a
$\chi^2(1)$-distribution under the null hypothesis, makes it straightforward to
compute the Type I error rate at level $\alpha_S$ for $c = 1$ as
\begin{eqnarray}\label{eq1:T1E}
\mbox{T1E} =   \left\{1-\Phi\left[2 \, \Phi^{-1}\left(1-\alpha_S \right)
 \right]\right\}/2.
\end{eqnarray}
For the golden level $\alpha_S =0.062$ at $\alpha = 0.025$, the Type I error
rate \eqref{eq1:T1E} is $0.0515$\%, slightly less than the Type I error rate
$\alpha^2=0.0625$\% of the two-trials rule. For comparison, the Type I error
rate at the nominal level $\alpha_S=0.025$ is $0.0022$\%, much smaller than
0.0625\%.

For $c \neq 1$, the Type I error rate can be calculated through numerical
integration:
\begin{equation}\label{eq1:T1E0}
  \mbox{T1E} = \int_{z_{\alpha_S}}^{\infty}
\P(z_r \geq \zrmin \given z_o, c, \alpha_S) \,
  \phi(z_o) \, dz_o,
\end{equation}
where $\phi(\cdot)$ denotes the standard normal density function. The first term
in the integral of \eqref{eq1:T1E0} is the probability of replication success at
level $\alpha_S$ conditional on a fixed original test statistic $z_o$ and a
relative sample size $c$. Now $z_r \sim \Nor(0,1)$ under the null hypothesis, so
this term simplifies to
$\P(z_r \geq \zrmin \given z_o, c, \alpha_S) = 1 - \Phi(\zrmin)$ where $\zrmin$
in \eqref{eq1:eq.z} depends on $z_o$, $c$, and $\alpha_S$.

@@

The left plot in Figure \ref{fig1:fig4} displays the Type I error rate for
$\alpha=0.025$ as a function of the relative sample size $c$. It can be seen
that the Type I error of the replication success approach decreases with
increasing relative sample size $c$. This also follows from \eqref{eq1:T1E0}
where \mbox{$\P(z_r \geq \zrmin \given z_o, c, \alpha_S) = 1 - \Phi(\zrmin)$}
decreases with increasing $c$, because $\zrmin$ increases with increasing $c$,
see equation \eqref{eq1:eq.z}.

@@

The project power for replication success is computed as
\begin{equation*}
  \mbox{PP} = \int_{z_{\alpha_S}}^{\infty}
\P(z_r \geq \zrmin \given z_o, c, \alpha_S) \,
  \phi(z_o - \mu) \, dz_o
\end{equation*}
and shown in the right plot of Figure \ref{fig1:fig4} as a function of $c$. For
the golden level, the project power quickly increases to values above 90\%,
whereas the nominal level only reaches around 80\% project power. The project
power based on the two-trials rule is shown for comparison, which is always
smaller than for the golden level and converges to 90\% for large $c$.

@@

Figure~\ref{fig1:fig6} displays the relative effect size $d$ versus the original
$p$-value $p_o$ for each study pair and stratified by project. Note that one
study pair from the Philosophy project is not shown due to extremely small
original $p$-value and another study pair from the Psychology project is not
shown due to a very large relative effect size. We can see that for most of the
study pairs, the replication success approach and the two-trials rule lead to
the same conclusion, only six replications show conflicting results. They are
highlighted with diamonds in Figure~\ref{fig1:fig6} and their characteristics are
summarised in Table~\ref{tbl:discrep}.
\begin{table}[!ht]
    \centering
  \caption{Characteristics of studies for which the replication success approach
    (at the golden level) and the two-trials rule disagree (at one-sided
    $\alpha = 0.025$). Shown are relative sample size $c$, relative effect size
    $d$, original, replication and recalibrated sceptical $p$-value $p_o$, $p_r$
    and $\tilde{p}_S$.}
  \label{tbl:discrep}
\resizebox{\textwidth}{!} {
% latex table generated in R 4.0.5 by xtable 1.8-4 package
% Fri Nov 25 12:12:30 2022
\begin{tabular}{lllllll}
  \toprule
Study & Project & $c$ & $d$ & $p_o$ & $p_r$ & $\tilde{p}_S$ \\
  \midrule
\citet{Schmidt2008} & Psychology & 2.58 & 1.28 & \textbf{0.028} & \textcolor{black}{< 0.0001} & \textcolor{black}{0.024} \\
  \citet{Oberauer2008} & Psychology & 0.60 & 0.67 & \textcolor{black}{0.0003} & \textbf{0.035} & \textcolor{black}{0.017} \\
  \citet{Payne2008} & Psychology & 2.65 & 0.41 & \textcolor{black}{0.001} & \textcolor{black}{0.023} & \textbf{0.031} \\
  \citet{Balafoutas2012} & Social Sciences & 3.48 & 0.52 & \textcolor{black}{0.009} & \textcolor{black}{0.011} & \textbf{0.04} \\
  \citet{Pyc2010} & Social Sciences & 9.18 & 0.38 & \textcolor{black}{0.011} & \textcolor{black}{0.004} & \textbf{0.061} \\
  \citet{Nichols2006} & Experimental Philosophy & 9.40 & 0.49 & \textcolor{black}{0.015} & \textcolor{black}{0.0006} & \textbf{0.049} \\
   \bottomrule
\end{tabular}%
}
\end{table}
Two studies from the Psychology project show replication success but fail the
two-trials rule. These studies show $p$-values that are slightly above the
significance threshold in either original or replication study, but do not
exhibit much shrinkage; in the replication of \citet{Oberauer2008}, the
replication $p$-value was $p_r = 0.035$, a little too large to pass the
two-trials rule. However, as the replication effect estimate shrunk only about
$30$\% compared to the original one, replication success is still achieved.
Conversely, the original $p$-value $p_o = 0.028$ in \citet{Schmidt2008} was just
above the significance level, yet the replication led to a highly significant
result $p_r < 0.0001$ with the effect estimate being even $30$\% larger than the
original counterpart, which therefore also resulted in replication success.

>>>>

\textbf{Key words}: Power, replication studies, sceptical $p$-value, shrinkage,
two-trials rule, Type I error rate

@@

\begin{center}
\begin{figure}[!h]
\begin{center}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
{\centering \includegraphics[width=\maxwidth]{images/paper1/fig1-1}
}
\end{knitrout}
\caption{Example of the assessment of replication success. The original study
  from \citet{Pyc2010} has effect estimate $\hat \theta_o= 0.4$ on Fisher's $z$
  scale (95\% CI from $0.05$ to $0.74$) and one-sided $p$-value
  \mbox{$p_o = 0.011$}. The left part of the figure illustrates the
  reverse-Bayes derivation of the sufficiently sceptical prior based on the
  original study result and the posterior with lower credible limit fixed at
  zero. The comparison of the sufficiently sceptical prior with the replication
  study result ($\hat \theta_r = 0.15$, 95\% CI from 0.04 to 0.26,
  $p_r = 0.004$) in the right part of the figure is used to assess potential
  prior-data conflict.}
  \label{fig1:fig1}
\end{center}
\end{figure}
\end{center}

@@

The actual value of $p_{\mbox{\scriptsize Box}}$ is difficult to interpret as it
depends on the level $\alpha$ and does not even exist if the original $p$-value
$p_o$ exceeds $\alpha$. However, \citet{Held2020} showed that if both
$\sign(z_o)=\sign(z_r)$ and
\begin{equation}\label{eq1:extrinsic.p}
\left({z_o^2}/{z_{{\alpha_{\mathrm{S}}}}^2}-1 \right) \left({z_r^2}/{z_{{\alpha_{\mathrm{S}}}}^2}
- 1 \right) \geq c
\end{equation}
hold, replication success at level ${\alpha_{\mathrm{S}}}$ is achieved, where
$z_{{\alpha_{\mathrm{S}}}} = \Phi^{-1}(1-{\alpha_{\mathrm{S}}})$. The
requirement \eqref{eq1:extrinsic.p} can be assessed for any value of
${{\alpha_{\mathrm{S}}}} > \max\{p_o, p_r\}$ and of particular interest is the
smallest possible value of $\alpha_{\mathrm{S}}$ where \eqref{eq1:extrinsic.p}
holds, the so-called \textit{sceptical $p$-value} $\ps$. We are thus interested
in the value $z_{\mathrm{S}}^2$ that fulfills
\begin{equation}\label{eq1:extrinsic.p2}
\left({z_o^2}/{z_{\mathrm{S}}^2}-1 \right) \left({z_r^2}/{z_{\mathrm{S}}^2}
- 1 \right) = c.
\end{equation}
There is a unique solution of \eqref{eq1:extrinsic.p2} which defines the
one-sided {sceptical $p$-value} $\ps= 1-\Phi\left({z_{\mathrm{S}}}\right)$ where
$z_{\mathrm{S}} \coloneqq + \surd z_{\mathrm{S}}^2$, provided
$\sign(z_o)=\sign(z_r)$ holds. Replication success at level
$\alpha_{\mathrm{S}}$ is then achieved if $\ps \leq \alpha_{\mathrm{S}}$. In the
introductory example based on the original study by \citet{Pyc2010}, the
sceptical $p$-value turns out to be $\ps=0.11$.

The sceptical $p$-value has a number of interesting properties, see
\citet[Section 3.1]{Held2020} for details. In particular,
$\ps > \max\{p_o, p_r\}$ always holds with $\ps \downarrow \max\{p_o, p_r\}$ for
$c \downarrow 0$. Furthermore, if the $p$-values $p_o$ and $p_r$ are fixed, the
sceptical $p$-value $\ps$ increases with decreasing relative effect size $d$.
The first property ensures that both the original and the replication study have
to be sufficiently convincing on their own to achieve replication success. The
second property guarantees that shrinkage of the replication effect estimate is
penalized.

The level for replication success $\alpha_{\mathrm{S}}$ has to be distinguished
from the significance level $\alpha$ associated with the ordinary $p$-value.
\citet{Held2020} has used the \textit{nominal level} for replication success
($\alpha_{\mathrm{S}}=\alpha$) for convenience, but in the following we will
propose a recalibration of the procedure along with a new value for
$\alpha_{\mathrm{S}}$, the \textit{golden level}
(Section~\ref{sec1:goldenthresh}). The derivation is based on a property of the
required relative effect size for replication success, if the relative sample
size is very large (Section~\ref{sec1:res}). In a nutshell, the golden level
ensures that for original studies which were only borderline significant
($p_o=\alpha$), replication success is only possible if the replication
effect estimate is larger than the original one ($d > 1$).\\

\subsection{Relative effect size}\label{sec1:res}
Without loss of generality we now assume that $\hat \theta_o > 0$ and that
$p_o < {\alpha_{\mathrm{S}}}$ has been observed in the original study, otherwise
it would be impossible to achieve replication success at level
$\alpha_{\mathrm{S}}$ because $\ps$ is always larger than $p_o$. The condition
\eqref{eq1:extrinsic.p} for replication success can then be re-written as
\begin{equation}\label{eq1:eq.z}
  z_r \geq   z_{{\alpha_{\mathrm{S}}}} \sqrt{1+c/(K-1)} \eqqcolon  \zrmin,
\end{equation}
where $K=z_o^2/z_{{\alpha_{\mathrm{S}}}}^2>1$. The right hand-side of
\eqref{eq1:eq.z} is the minimum replication $z$-value $\zrmin$ required to
achieve replication success. Note that $\zrmin$ increases with increasing $c$,
so increasing the replication sample size leads to a more stringent success
requirement $z_r$ and the corresponding replication $p$-value $p_r$.

@@

\subsection{The golden level}\label{sec1:goldenthresh}
Significance of both the original and the replication study at level $\alpha$ is
a necessary but not sufficient requirement for replication success at the
nominal level ($\alpha_{\mathrm{S}} = \alpha$). The nominal level may therefore
be too stringent. It is more reasonable to calibrate the procedure in such a way
that to establish replication success, original and replication study do not
both necessarily need to be significant at level $\alpha$, provided that the
replication effect estimate does not shrink compared to the original one. We
therefore choose a level $\alpha_{\mathrm{S}}$ such that a borderline
significant original study ($p_o = \alpha$) cannot lead to replication success
if there is shrinkage $s > 0$ of the replication effect estimate.
Mathematically, this translates to setting $\dinfty = 1$ and
\mbox{$K = z_\alpha^2/z_{\alpha_{\mathrm{S}}}^2$}
in~\eqref{eq1:smallestpossible} and leads to the quadratic equation $K(K-1) = 1$
with solution $K = \varphi$ where \mbox{$\varphi = (\sqrt{5}+1)/2 \approx 1.62$}
is known as the golden ratio. Solving for $z_{\alpha_{\mathrm{S}}}$ gives
$z_{\alpha_{\mathrm{S}}} = z_\alpha / \sqrt{\varphi}$ and the corresponding
\textit{golden level}
\begin{eqnarray}\label{eq1:golden}
\alpha_{\mathrm{S}} & = & 1 -  \Phi(z_\alpha / \sqrt{\varphi} )
\end{eqnarray}
for replication success. This is our recommended default choice to assess
replication success and we will study its properties in the following in more
detail. For $z_\alpha = 1.96$ (one-sided $\alpha = 0.025$), the golden level is
$\alpha_{\mathrm{S}} =0.062$. In the introductory example shown in Figure
\ref{fig1:fig1}, the sceptical $p$-value is $\ps=0.11 > 0.062$, so the
replication of the \citet{Pyc2010} study was not successful.

The golden level \eqref{eq1:golden} is derived from~\eqref{eq1:smallestpossible}
with $\dinfty = 1$. However, we may also use a different value for the limiting
relative effect size $\dinfty$, say $\dinfty=0.8$. Then replication success is
only possible for a borderline significant result ($p_o = \alpha$) if there is
less than $1-\dinfty$ (20\% for \mbox{$\dinfty=0.8$}) shrinkage of the
replication effect estimate. This approach is equivalent to a limiting relative
effect size of 1 if the original $p$-value $p_o$ is equal to a different level
$\alpha'$, which can be derived as follows: First, solving
\eqref{eq1:smallestpossible} for $\dinfty > 0$ gives
$K = z_\alpha^2/z_{\alpha_{\mathrm{S}}}^2 = 1/2+\sqrt{1/4 + 1/\dinfty^2}$. The
new level~$\alpha'$ fulfills $\varphi=z_{\alpha'}^2/z_{\alpha_{\mathrm{S}}}^2$,
so $z_\alpha^2/K=z_{\alpha'}^2/\varphi$ and therefore
\begin{equation}\label{eq1:alphaPrime}
\alpha' = 1-\Phi\left(z_{\alpha} \, \sqrt{\varphi / K} \right).
\end{equation}
For example, for $\alpha = 0.025$ and $\dinfty = 0.8$ we obtain $\alpha'=0.033$.

@@

\sloppy The condition $\ps \leq \alpha_{\mathrm{S}}$ for replication success at the
golden level is equivalent to
\mbox{$z_{\mathrm{S}} \geq z_\alpha / \sqrt{\varphi}$}, \ie{}
$z_{\mathrm{S}} \sqrt{\varphi} \geq z_\alpha$. In practice it may be preferable
to recalibrate the sceptical $p$-value \mbox{$\ps = 1 - \Phi(z_{\mathrm{S}})$}
to $ \tilde{p}_{\mathrm{S}} = 1 - \Phi(z_{\mathrm{S}} \sqrt{\varphi})$, which
then needs to be compared to $\alpha$ (rather than $\alpha_{\mathrm{S}}$) to
assess replication success and can thus be interpreted on the same scale as an
ordinary $p$-value. For example, the recalibrated sceptical $p$-value for the
replication of \citet{Pyc2010} turns out to be $\tilde{p}_{\mathrm{S}}=0.061$
and does not lead to replication success at any level $\alpha<0.061$, including
the standard $0.025$ level.

@@

\begin{figure}[!h]
\centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
{\centering \includegraphics[width=\maxwidth]{images/paper1/fig2-1}
}
\end{knitrout}
\caption{Comparison of replication success at the golden level
  ($\ps \leq \alpha_{\mathrm{S}} = 0.062$) and the two-trials rule
  (\mbox{$p_o \leq 0.025$} and $p_r \leq 0.025$). The dotted areas indicate that
  success is impossible for original \mbox{$p$-value $p_o$} and relative effect
  size $d$. In the white areas success is possible and depends on the relative
  sample size $c$ as indicated by the grey lines. The dashed black line in the
  left plot indicates the limiting relative effect size $\dinfty$. }
\label{fig1:fig2}
\end{figure}

@@

For $c=1$, \citet[Section 3]{Held2020} showed that $z_{\mathrm{S}}^2$ in
\eqref{eq1:extrinsic.p2} simplifies to half the harmonic mean of the squared
test statistics $z_o^2$ and $z_r^2$. The connection
$z_{\mathrm{S}}^2 = z_{\mathrm{H}}^2/4$ to the harmonic mean $\chi^2$-test
statistic $z_{\mathrm{H}}^2$ \citep{Held2020b}, which has a
$\chi^2(1)$-distribution under the null hypothesis, makes it straightforward to
compute the Type I error rate at level $\alpha_{\mathrm{S}}$ for $c = 1$ as
\begin{eqnarray}\label{eq1:T1E}
\mbox{T1E} =   \left\{1-\Phi\left[2 \, \Phi^{-1}\left(1-\alpha_{\mathrm{S}} \right)
 \right]\right\}/2.
\end{eqnarray}
For the golden level $\alpha_{\mathrm{S}} =0.062$ at $\alpha = 0.025$, the Type I error
rate \eqref{eq1:T1E} is $0.0515$\%, slightly less than the Type I error rate
$\alpha^2=0.0625$\% of the two-trials rule. For comparison, the Type I error
rate at the nominal level $\alpha_{\mathrm{S}}=0.025$ is $0.0022$\%, much smaller than
0.0625\%.

For $c \neq 1$, the Type I error rate can be calculated through numerical
integration:
\begin{equation}\label{eq1:T1E0}
  \mbox{T1E} = \int_{z_{\alpha_{\mathrm{S}}}}^{\infty}
\P(z_r \geq \zrmin \given z_o, c, \alpha_{\mathrm{S}}) \,
  \phi(z_o) \, dz_o,
\end{equation}
where $\phi(\cdot)$ denotes the standard normal density function. The first term
in the integral of \eqref{eq1:T1E0} is the probability of replication success at
level $\alpha_{\mathrm{S}}$ conditional on a fixed original test statistic $z_o$ and a
relative sample size $c$. Now $z_r \sim \Nor(0,1)$ under the null hypothesis, so
this term simplifies to
$\P(z_r \geq \zrmin \given z_o, c, \alpha_{\mathrm{S}}) = 1 - \Phi(\zrmin)$ where $\zrmin$
in \eqref{eq1:eq.z} depends on $z_o$, $c$, and $\alpha_{\mathrm{S}}$.

@@

The left plot in Figure \ref{fig1:fig4} displays the Type I error rate for
$\alpha=0.025$ as a function of the relative sample size $c$. It can be seen
that the Type I error of the replication success approach decreases with
increasing relative sample size $c$. This also follows from \eqref{eq1:T1E0}
where \mbox{$\P(z_r \geq \zrmin \given z_o, c, \alpha_{\mathrm{S}}) = 1 - \Phi(\zrmin)$}
decreases with increasing $c$, because $\zrmin$ increases with increasing $c$,
see equation \eqref{eq1:eq.z}.

@@

The project power for replication success is computed as
\begin{equation*}
  \mbox{PP} = \int_{z_{\alpha_{\mathrm{S}}}}^{\infty}
\P(z_r \geq \zrmin \given z_o, c, \alpha_{\mathrm{S}}) \,
  \phi(z_o - \mu) \, dz_o
\end{equation*}
and shown in the right plot of Figure \ref{fig1:fig4} as a function of $c$. For
the golden level, the project power quickly increases to values above 90\%,
whereas the nominal level only reaches around 80\% project power. The project
power based on the two-trials rule is shown for comparison, which is always
smaller than for the golden level and converges to 90\% for large $c$.

@@

Figure~\ref{fig1:fig6} displays the relative effect size $d$ versus the original
$p$-value $p_o$ for each study pair and stratified by project. Note that one
study pair from the Philosophy project is not shown due to extremely small
original $p$-value and another study pair from the Psychology project is not
shown due to a very large relative effect size. We can see that for most of the
study pairs, the replication success approach and the two-trials rule lead to
the same conclusion, only six replications show conflicting results. They are
highlighted with diamonds in Figure~\ref{fig1:fig6} and their characteristics are
summarised in Table~\ref{tbl:discrep}.
\begin{table}[!ht]
    \centering
  \caption{Characteristics of studies for which the replication success approach
    (at the golden level) and the two-trials rule disagree (at one-sided
    $\alpha = 0.025$). Shown are relative sample size $c$, relative effect size
    $d$, original, replication and recalibrated sceptical $p$-value $p_o$, $p_r$
    and $\tilde{p}_{\mathrm{S}}$.}
  \label{tbl:discrep}
\resizebox{\textwidth}{!} {
% latex table generated in R 4.0.5 by xtable 1.8-4 package
% Fri Nov 25 12:12:30 2022
\begin{tabular}{lllllll}
  \toprule
Study & Project & $c$ & $d$ & $p_o$ & $p_r$ & $\tilde{p}_{\mathrm{S}}$ \\
  \midrule
\citet{Schmidt2008} & Psychology & 2.58 & 1.28 & \textbf{0.028} & \textcolor{black}{< 0.0001} & \textcolor{black}{0.024} \\
  \citet{Oberauer2008} & Psychology & 0.60 & 0.67 & \textcolor{black}{0.0003} & \textbf{0.035} & \textcolor{black}{0.017} \\
  \citet{Payne2008} & Psychology & 2.65 & 0.41 & \textcolor{black}{0.001} & \textcolor{black}{0.023} & \textbf{0.031} \\
  \citet{Balafoutas2012} & Social Sciences & 3.48 & 0.52 & \textcolor{black}{0.009} & \textcolor{black}{0.011} & \textbf{0.04} \\
  \citet{Pyc2010} & Social Sciences & 9.18 & 0.38 & \textcolor{black}{0.011} & \textcolor{black}{0.004} & \textbf{0.061} \\
  \citet{Nichols2006} & Experimental Philosophy & 9.40 & 0.49 & \textcolor{black}{0.015} & \textcolor{black}{0.0006} & \textbf{0.049} \\
   \bottomrule
\end{tabular}%
}
\end{table}
Two studies from the Psychology project show replication success but fail the
two-trials rule. These studies show $p$-values that are slightly above the
significance threshold in either original or replication study, but do not
exhibit much shrinkage; in the replication of \citet{Oberauer2008}, the
replication $p$-value was $p_r = 0.035$, a little too large to pass the
two-trials rule. However, as the replication effect estimate shrunk only about
$30$\% compared to the original one, replication success is still achieved.
Conversely, the original $p$-value $p_o = 0.028$ in \citet{Schmidt2008} was just
above the significance level, yet the replication led to a highly significant
result $p_r < 0.0001$ with the effect estimate being even $30$\% larger than the
original counterpart, which therefore also resulted in replication success.
